---
title: "Assign 2"
author: "Eduard Shokur"
date: "2/4/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(kableExtra)
library(pairwiseCI)
library(ggplot2)
options(scipen = 99, digits = 2)

```
## 1. Fish Diet:

 + A. This not an experiment or a retrospective study where history of risk factors to a disease was reviewed. Hence, this is prospective study because we study a group and collect data as events unfold.
 + B. This is a test of independence because test of homogeneity would be testing if the proportion of people who developed prostate cancer was the same regardless of amount of fish consumed. In this problem, however, we are testing, if there is association between amount of fish consumed prostate cancer.
 
 ``` {r} 
 tempTable <- as.table(rbind(c(110,2420,2769,507), c(14,201,209,42)))
dimnames(tempTable) <- list(Outcome = c("Cancer", "No_Cancer"),
                    Part_of_Diet = c("None"," Small Part of Diet", "Moderate Part", "Large Part"))

indFitTest <- chisq.test(tempTable)
residuals <-indFitTest$stdres

 ```
 + C. My NULL hypothesis is that there is no association between the amount of fish consumed and risk of developing prostate cancer. By alternative hypothesis, there is an association between amount of fish consumed and prostate cancer. Based on the Chi-Squared test's large p-value of `r indFitTest$p.value`, I fail to reject the NULL hypothesis. Also, standardized residuals are small. 
 
 + D. This study is not an experiment; therefore not causality can be inferred. Furthermore, if there was some causal relationship between amount of fish in diet, we might expect to see some indication of that in the relative risk proportions. In other words, as the amount of fish in diet becomes smaller (or larger, if that is the argument being made), the relative risk proportion should move accordingly. As can be seen in part E, no such connection between diet and relative risk proportion exists. 
  ``` {r}
  dataFrameTempTable <- tibble(Treatment=c("None","Small","Moderate", "Large"),Yes=tempTable[2,],No=tempTable[1,])

 rr <- pairwiseCI(cbind(Yes,No)~Treatment,data=dataFrameTempTable,method="Prop.ratio",
CImethod="Score",conf.level=1-.05/4, control="None")
plotCI(rr,lines=1,CIvert=TRUE,ylab="Confidence Interval of Relative Cancer Risk", main="Relative Risk by Amount of Fish in Diet")
 ```
 
 + E. We are 95% (simultaneous) confidence that compared to a group that consumes no fish, group of subjects that consumes large, moderate and small amounts of fish are `r rr$byout$lower[2]` to `r rr$upper[1]`, `r rr$byout$lower[2]` to `r rr$upper[1]` and `r rr$byout$lower[2]` to `r rr$upper[1]` times as likely to develop cancer respectively. Differing amounts of fish in the diet produce similar confidence level, which also throws doubts on the idea of causality.
 
 
## 2:
``` {r,fig.show='hold',out.width='50%'}
BodyFat <- read_csv("Body_fat_complete.csv")
ggplot(BodyFat,aes(x=Waist,y=Pct.BF))+geom_point()+ ggtitle("Percent Body Fat vs Waist Size With LS Line") + #plot points
        theme(plot.title = element_text(hjust = 0.50)) + # centers the title
#geom_smooth(se=FALSE, color="blue",linetype=2)+ # add loess smooth
geom_smooth(method=lm,se=FALSE)+ # add LS line
labs(y="% Body Fat",x="Waist Size")

resLine <- lm(Pct.BF~Waist, data=BodyFat)  # residual plot line
#dotplot of residuals
ggplot(BodyFat,aes(x=Pct.BF,y=resid(resLine))) + geom_point() + ggtitle("Plot of Residuals") + #plot points and add title
        theme(plot.title = element_text(hjust = 0.5)) + # centers the title 
geom_hline(yintercept=0,linetype="dashed") # residual plot
resid <- resid(resLine)  # predicted - actual
hist(resid, main = "Histogram of Residuals") #hisogram of the residuals
# data frame with prediction value based on whcih prediction interval will be made
predictionConfValuesDF <- data.frame(Waist=c(40))
# gives confidence interval for prediction of mean
predictdMuInt <- predict(resLine,newdata=predictionConfValuesDF,interval="confidence") # m1 contains lm fit
# gives confidence interval for prediction of prediction interval
predictInt <- predict(resLine,newdata=predictionConfValuesDF,interval="prediction") # m1 contains lm fit
```

+ A. The "straight enough" condition is satisfied. The residuals are randomly distributed. Histogram is not quite symmetrical. If we use t procedures, because the sample size is quite large, linearity assumptions are satisfied well enough!

 + B. The slope of the LS line of the model is `r coef(resLine)[2]`. This means that for every additional inch of wasit, the body fat increases by `r coef(resLine)[2]` percent. We are 95% confident that for every additional inch of waist size, the percent body fat goes up by anywhere between `r confint(resLine)[2]` and `r confint(resLine)[4]` inches.
 
 + C. Based on the model made, on average a man with 40 inch waist has body composition that is `r predictdMuInt[1]` percent fat . I am 95% confident that on average the same man has a body composition of anywhere between `r predictdMuInt[2]` and `r predictdMuInt[3]` body fat.
 
 + D. Based on the model made, the man with 40 inch waist has body composition that is `r predictInt[1]` percent fat . I am 95% confident that the same man (individual) has a body composition of anywhere between `r predictInt[2]` and `r predictInt[3]` body fat.
 